Fixing Vulnerabilities Hinders Maintainability

### 2019-01-31 paper/ICPC19/icpc19.tex
more results

Regarding security commits results, we observe that maintainability decreases in 40.20\% (244), increases in 29.33\% (178) and stays the same in 30.5\% (185) of the cases after security refactorings being applied. The resulting p-value of the Wilcoxon signed-rank test is $1.21$x$10^{-10}$. Since the p-value is below the significance level of $0.05$, it is fair to state that \emph{security refactorings have a negative impact in the maintainability of open-source software}.

For regular commits, we also observe that maintainability decreases in 41.35\% (251) of the cases after regular refactorings being applyed. But in contrast to security commits, it increases in 58.16\% (353) and stays the same in 0.5\% (3). The resulting p-value of the Wilcoxon signed-rank test is $1.54$x$10^{-6}$. Since the p-value is below the significance level of $0.05$, it is fair to state that \emph{regular refactorings have a positive impact in the maintainability of open-source software}.

@@

>>>>

Regarding security commits results, we observe that maintainability decreases 
in 40.20\% (244), stays equal in 30.5\% (185) and increases in 29.33\% (178)  
of the cases after security refactorings being applied. The resulting p-value 
of the Wilcoxon signed-rank test is $1.21$x$10^{-10}$. Since the p-value is below 
the significance level of $0.05$, it is reasonable to affirm that \emph{security 
refactorings have a negative impact in the maintainability of open-source software}.

For regular commits, we also observe that maintainability decreases in 41.35\% 
(251) of the cases after regular refactorings being applyed. But in contrast 
to security commits, it increases in 58.16\% (353) and stays equal in 0.5\% 
(3) of the cases. The resulting p-value of the Wilcoxon signed-rank test is 
$1.54$x$10^{-6}$. Since the p-value is below the significance level of $0.05$, 
it is reasonable to affirm that \emph{regular refactorings have a positive 
impact in the maintainability of open-source software}.

@@

In this study, we also evaluated the impact of each programming language on the 
maintainability of open-source software, Figure \ref{fig:lang}. Although the
dataset contains security refactorings for more than $13$ languages, we only
present the results for \emph{Java}, \emph{C}, \emph{Ruby} and \emph{PHP} because
one of the requirements of the Wilcoxon signed-rank test is that the input sample
has to have more than $20$ measurements. The other languages were integrated in the
\emph{Others} set. The results of the Wilcoxon signed-rank test by pattern returned 
statistical evidence which supports that the maintainability of open-source software 
decreases for security refactorings in 3 different languages: \emph{C} 
(p = $5.72$x$10^{-9}$), Ruby (p = 0.057) and PHP (p = $3.54$x$10^{-6}$). The results 
also provide statistical significance for when security refactorings are performed
in \emph{Java} (p = $3.61$x$10^{-2}$). \emph{Python} and the other languages 
that integrate the \emph{Others} set contain more cases where the maintainability
increases. However, the results obtained for these patterns are not statistically 
significant.
